---
title: "Reddit Imgur Animation"
author: "Max Woolf (@minimaxir)"
date: "2019-11-11"

---

## Setup

```{r}
library(tidyverse)
library(lubridate)
library(gganimate)

sessionInfo()
```

```{r}
theme_set(
  theme_minimal(base_size = 7, base_family = "Source Sans Pro") +
    theme(
      plot.title = element_text(
        family = "Source Sans Pro Bold",
        margin = margin(t = 0.0, b = 0.1, unit = 'cm'),
        size = 8
      ),
      plot.subtitle = element_text(
        family = "Source Sans Pro Semibold",
        color = "#969696",
        size = 6
      ),
      plot.caption = element_text(color = "#969696"),
      legend.title = element_text(family = "Source Sans Pro Bold",
                                  size = 15),
      legend.key.width = unit(0.25, unit = 'cm'),
      legend.spacing.x = unit(0.1, 'cm'),
      legend.margin = margin(l = 0),
      strip.text = element_text(
        size = 4.25,
        family = "Roboto Condensed Bold",
        color = "#000000"
      ),
      axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      panel.grid = element_blank()
    )
)
```

Manually specify the colors and order for each level. Colors adapted from the [Flat UI Colors](https://flatuicolors.com/palette/defo) palette.

```{r}
fill_colors <- c(
  "Reddit" = "#f39c12",
  "Imgur" = "#27ae60",
  "Gfycat" = "#c0392b",
  "Giphy" = "#8e44ad",
  "Flickr" = "#2c3e50",
  "Tumblr" = "#16a085",
  "Instagram" = "#d35400",
  "Facebook" = "#2980b9",
  "Other" = "#7f8c8d"
)
```


# Load data

Encode the website domains as a factor to order them in the same order as above.

```{r}
df <- read_csv('results-20191118-201411.csv') %>%
  mutate(website = factor(website, levels=names(fill_colors)))

df %>% head()
```

# Static Output

Use a static output for testing.

```{r}
filter_date <- '2019-08-01'

plot <-
  ggplot(df %>% filter(month == filter_date),
         aes(
           x = 0,
           y = num_submissions,
           fill = website
         )) +
  geom_bar(stat = "identity", position=position_fill(reverse = TRUE)) +
  coord_flip() +
  scale_fill_manual(values=fill_colors) +
  labs(
    title = "The Rise (and Fall) of Imgur on Reddit Over Time",
    subtitle = "Charts display proportions of all submissions to subreddit linking to website at month/year. Data via Pushshift/BigQuery. Made with R/ggplot2",
    fill = format(as.Date(filter_date), "%b\n%Y\n"),
    caption = 'Max Woolf — minimaxir.com'
  ) +
  facet_wrap(~ subreddit, ncol=10)

ggsave('reddit_imgur_static.png',
       plot,
       width = 1920/300,
       height = 1080/300)
```

# Animation

gganimate is overkill, so save each frame and stitch them together using ffmpeg.

```{r}
frame_path <- "/Users/maxwoolf/Desktop/reddit-imgur/"
```


```{r}
months <- df %>% pull(month) %>% unique()

months %>% head()
```

```{r}
render_month <- function(i, frame_path) {

filter_date <- months[i]  

frame <-
  ggplot(df %>% filter(month == filter_date),
         aes(
           x = 0,
           y = num_submissions,
           fill = website
         )) +
  geom_bar(stat = "identity", position=position_fill(reverse = TRUE)) +
  coord_flip() +
  scale_fill_manual(values=fill_colors) +
  labs(
    title = "The Rise (and Fall) of Imgur on Reddit Over Time",
    subtitle = "Charts display proportions of all submissions to subreddit linking to website at month/year. Data via Pushshift/BigQuery. Made with R/ggplot2.",
    fill = format(filter_date, "%b\n%Y\n"),
    caption = 'Max Woolf — minimaxir.com'
  ) +
  facet_wrap(~ subreddit, ncol=10)

ggsave(paste0(frame_path, i, ".png"),
     frame,
     width = 1920/300,
     height = 1080/300)
}

render_month(1, frame_path)
```

```{r}
system.time(temp <- map(1:length(months), render_month, frame_path=frame_path))
```

The images are rendered to a video using `ffmpeg`:

`ffmpeg  -i %d.png -c:v libx264 -vf fps=4 -pix_fmt yuv420p out.mp4`

# LICENSE

MIT License

Copyright (c) 2019 Max Woolf

Permission is hereby granted, free of charge, to any person obtaining a copy
of this software and associated documentation files (the "Software"), to deal
in the Software without restriction, including without limitation the rights
to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
copies of the Software, and to permit persons to whom the Software is
furnished to do so, subject to the following conditions:

The above copyright notice and this permission notice shall be included in all
copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
SOFTWARE.